Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms.tex
replace fig name with . to _
update keywwords

\keywords{ISM: molecules --
          infrared: galaxies --
          galaxies: mergers --
          galaxies: starburst --
          galaxies: evolution --
          quasars: individual (RXS\,J1131$-$1231)}

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

>>>>

\keywords{infrared: galaxies --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          quasars: individual (RXS\,J1131$-$1231) --
          radio lines: ISM}

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}
